### 2020-09-15 latex/acrobot.tex
UPdated introduction to acrobot and added simple acrobot

\begin{figure}
    \centering
    % TODO include acrobot model image
    \caption{The acrobot model.}%
    \label{fig:acrobot-model}
\end{figure}

@@

In gymnastics terminology, a ``giant" is when the gymnast performs full
rotations around the bar with their body almost fully extended
\cite{usagym_giant}. We are interested in studying the energy stabilization
problem for the acrobot by using VNHCs to generate giant motion. The control of
giant motion for the acrobot has been studied thoroughly 
\cite{energy_pumping_robotic_swinging, swingup_giant_acrobot,
control_giant_two_link_gymnastic_robot}, including several studies which use
virtual (holonomic) constraints to achieve this
\cite{dynamical_servo_acrobot_vc, control_giant_two_link_gymnastic_robot,
xingbo_thesis}. However, these controllers are not intuitive nor easy to design:
\cite{control_giant_two_link_gymnastic_robot} defines a constraint by inverting
a trajectory in time onto the state space; \cite{dynamical_servo_acrobot_vc}
requires a cascade controller to stabilize both a constraint and a desired limit
cycle in the state space; and \cite{xingbo_thesis} enforces the giant by adding
an extra state to estimate the velocity, which is a crude attempt at using
VNHCs.

In this chapter we will design a VNHC which can generate giant motion using much
more intuitive methods. In the process of proving that this VNHC injects energy,
we will also show a promising method for generating desirable VNHCs in the
future.

\section{Dynamics of the Acrobot}
% TODO: Derive the acrobot dynamics in Hamiltonian form
\section{Previous Approaches}
% TODO: Give Xingbo's intuition, abstract away to qa = sin(theta) constraint
% based on VLP but show it doesn't work well in our framework
% TODO: Describe Xingbo's results and observe that his results were similar to a VNHC
% except they used VHC tools. We will modify his approach to use VNHCs and prove
% rigorously that we can stabilize any energy level set on the acrobot.

>>>>

\begin{figure}
    \centering
    \includestandalone[width=0.7\textwidth]{images/acrobot_model}
    \caption{The acrobot model.}%
    \label{fig:acrobot-model}
\end{figure}

@@

In gymnastics terminology, a ``giant" is when the gymnast performs full
rotations around the bar with their body almost fully extended
\cite{usagym_giant}. We are interested in studying the energy stabilization
problem for the acrobot by using VNHCs to generate giant motion. The control of
giant motion for the acrobot has been studied thoroughly 
\cite{energy_pumping_robotic_swinging, swingup_giant_acrobot,
control_giant_two_link_gymnastic_robot}, including several studies which use
virtual (holonomic) constraints to achieve this behaviour
\cite{dynamical_servo_acrobot_vc, control_giant_two_link_gymnastic_robot,
xingbo_thesis}. However, these controllers are neither intuitive nor easy to design:
\cite{control_giant_two_link_gymnastic_robot} defines a constraint by inverting
a trajectory in time onto the state space; \cite{dynamical_servo_acrobot_vc}
requires a cascade controller to stabilize both a constraint and a desired limit
cycle in the state space; and \cite{xingbo_thesis} enforces the giant by adding
an extra state to estimate the velocity, which increases the dimensionality of
the problem as a crude approach to using VNHCs.

In this chapter we will design a physically-intuitive VNHC which generates giant
motion. We will prove that this VNHC injects energy into the acrobot;
in the process of completing this proof,
we will describe a promising method which may be used to generate desirable 
VNHCs in the future.

\section{Dynamics of the Acrobot}
% TODO: Derive the acrobot dynamics in Hamiltonian form
For the acrobot model displayed in Figure \ref{fig:acrobot-model}, 
the COM of each link lies somewhere along the link itself. 
While this is the most general representation of an acrobot, the dynamics are
somewhat complicated and are difficult to use when proving the results in the 
rest of this chapter. For simplicity, we will
assume the acrobot is comprised of two massless rods of equal length with 
equal masses at the tips, as in Figure \ref{fig:simple-acrobot-model}; we call
this a \textbf{simple} acrobot.

\begin{figure}
    \centering
    \includestandalone[width=0.5\textwidth]{images/simple_acrobot_model}
    \caption{A simple acrobot with lengths \(l\) and masses of size \(m\).}
    \label{fig:simple-acrobot-model}
\end{figure}

\section{Previous Approaches}
% TODO: Give Xingbo's intuition, abstract away to qa = sin(theta) constraint
% based on VLP but show it doesn't work well in our framework
% TODO: Describe Xingbo's results and observe that his results were similar to a VNHC
% except they used VHC tools. We will modify his approach to use VNHCs and prove
% rigorously that we can stabilize any energy level set on the acrobot.
